### 2014-11-21 src/2_Finance.tex
avance 20

>>>>

A trade consists at least of two orders: one to enter the market (buy order) and
exit the market (sell order). Traders have different types of order they can
execute:

\begin{description}
\item[Market order:] allow to buy or sell an asset at the current best price
whatever that price is. The transaction price is determined by the market
considering previous executed orders and volume requested.
\item[Limit order:] allow to specify the price you want to buy or sell an asset.
Depending on the market conditions, this type of orders can neven be executed.
\item[Stop order:] are suitable for investors who are unable to monitor their
investments for a period of time. Stop order allow to specify the price that a
position should be closed called stop price. When the stop price is reached a
market order is executed, this means that market price won't be exactly the same
specified in the stop order.
\end{description}

In terms of commissions, limit order are more expensive than market orders and
there is no certainty of execution.

Moreover, all orders can specify other parameters such as:

\begin{description}
\item[Fill or Kill:] is an order that must be executed inmediately or being
cancelled, no partial fulfillments are allowed. 
\item[Day:] the order is only valid during the day.
\item[Good til canceled:] a order is active until the investor decides to cancel
ir or the trade is executed.
\end{description}

In order to determine the execution price, buyers and sellers orders are placed
in an order book which help to determine which order can be fulfilled.
Figure~\ref{fig:orderbook} illustrates how buyers and sellers are ordered. The
ask or offer price is the current lower price a seller is willing to accept for
a good. The bid price corresponds to the current highest price a buyer is
willing to pay for a good. Orders with the same price are prioritorized by
arrival time and placed on top of the book.  The difference between ask and bid
price is called spread.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.5\textwidth]{img/orderbook}
  \caption{Order book. Buyers and sellers are ordered according to the bid or
  ask price and the market determines the mid-price and transacted volume.}
  \label{fig:orderbook}
\end{figure}

Today, order books are available and they are a popular source of study among
researchers. To determine the mid-price and spread modeling are some of the
problems studied.
